% 
% Introduction
% @author Pieter Maene <pieter.maene@student.kuleuven.be>
%

\section{Introduction}

Elections are an important part of our democratic society. In 2014, national elections will be held in 40 countries and 42\% of the world population will be able to cast its vote.\cite{news:economist_2014_ballot_boxes} It is therefore necessary to have a trustworthy voting system. In current systems, voters usually have to trust the election organiser. Voter-verifiable systems allow them to verify whether their ballot was registered correctly and check the election result. Helios is such a voter-verifiable system, that can be used for online elections. It is an open-source project developed by Ben Adida.\cite{site:adida_helios_documentation} Robbert Coeckelbergh added threshold encryption to it, so that one trustee can no longer stall the election.\cite{coeckelbergh_application_and_extension_of_the_helios_voting_system} Online elections can only be used in situations where coercion is not a big threat, though. 

\par The Web Cryptography API is a new W3C specification that will add native cryptographic functionality to user agents.\cite{sleevi_watson_web_cryptography_api} It could improve the usability of web applications that need user-level cryptography. The performance of this new API is compared to that of existing JavaScript cryptography libraries.

\par This paper will discuss the procedure that should be followed to organise an election in Helios (\ref{sec:procedure}). The interface of the system was also modified to better support this procedure and improve its usability (\ref{sec:user_interface_improvements}). In \ref{sec:web_cryptography_api} the performance of the new Web Cryptography API is analysed. Finally, the system was deployed in a production environment and applied in an actual election (\ref{sec:board_election}).